### 2018-04-30 paper/file-exchange-design.tex
minor

As stated above, Alice and Bob exchange some limited data out-of-bound using 
their smartphones.
The information they will exchange is the following:
\begin{enumerate}
  \item Bob creates an onion route header, \(H_\rdv\), by running 
    \([\Recv]\) %(\cref{SPORRecv}) 
    and gives it to Alice.
  \item Alice gives Bob number of file chunks, \(n\), and the size of the file 
    chunks.
  \item They agree on a file-specific key \(k\) for some (authenticated) 
    encryption scheme \(\Enc*\).
\end{enumerate}
Then Alice encrypts the file \(f\) and receives the ciphertext \(c_f\gets 
  \Enc*[Enc](k, f)\).
She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
and runs \([\Send](H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
parallel.
\commentDaniel{Or shall we do it sequentially?}

>>>>

As stated above, Alice and Bob exchange some limited data out-of-bound using 
their smartphones.
The information they will exchange is the following:
\begin{enumerate}
  \item Bob creates an onion route header, \(H_\rdv\), by running 
    \([\Recv]\) %(\cref{SPORRecv}) 
    and gives it to Alice.
  \item Alice gives Bob number of file chunks, \(n\), and the size of the file 
    chunks.
  \item They agree on a file-specific key \(k\) for some (authenticated) 
    encryption scheme \(\Enc*\).
\end{enumerate}
Then Alice encrypts the file \(f\) and receives the ciphertext \(c_f\gets 
  \Enc*[Enc](k, f)\).
She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
and runs \(\Send(H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
parallel.
\commentDaniel{Or shall we do it sequentially?}

### 2018-04-30 paper/message-passing-design.tex
minor

Once Alice get the \(H_\rdv\), Alice uses \([\Send]\) at some
later time to send the message to Bob using any of her devices from
its \squad.% (See \cref{SPORSend}). 
First, \([\Send]\) extends the route
\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
chosen). Second, \([\Send]\) extracts from the onion the first
layer, which contained the overall
possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
One device from $D$ is randomly chosen, and the \([\Fwd]\)
sub-function is called as long as the message forwarding to one node of
the next layer is not successful.% (See \cref{SPORFwd}). 
Along the path, each node decrypts
in sequence the different layer with the current node’s private key. 
The end of the route is reached when special value \(H_\rdv = \top\) is
encountered. Consequently the ciphered message \(c_m\) is then stored
in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).

@@

\begin{figure}[t]
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    %\Require{$\pk, \sk$ is the public--private key-pair of the node.}
    \Function{[\Fwd]}{$C_H, m$}
      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat C_H'\gets H$
      \If{$C_H' = \top$}
        \State \Return $\Store[m]$
      \EndIf
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H', m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}

  \begin{algorithmic}[1]
    \Function{\Store}{$m$}
      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
      \If{$m = \bot$}
        \State \Return $\bot$
      \EndIf
      \State Store $m$ to disk.
      \State \Return $\top$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
  \caption{\label{SPORFwd}%
    The \([\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
    by decrypting \(C_H\) with the node's associated private key.
    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
    is intended for the local node and \(c_m\) is instead sent to disk using 
    \(\Store\).% (\cref{SPORRecv}).%
  }
\end{figure}

>>>>

Once Alice get the \(H_\rdv\), Alice uses \([\Send]\) at some
later time to send the message to Bob using any of her devices from
its \squad.% (See \cref{SPORSend}). 
First, \([\Send]\) extends the route
\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
chosen). Second, \(\Send\) extracts from the onion the first
layer, which contained the overall
possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
One device from $D$ is randomly chosen, and the \(\Fwd\)
sub-function is called as long as the message forwarding to one node of
the next layer is not successful.% (See \cref{SPORFwd}). 
Along the path, each node decrypts
in sequence the different layer with the current node’s private key. 
The end of the route is reached when special value \(H_\rdv = \top\) is
encountered. Consequently the ciphered message \(c_m\) is then stored
in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).

@@

\begin{figure}[t]
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    %\Require{$\pk, \sk$ is the public--private key-pair of the node.}
    \Function{\Fwd}{$C_H, m$}
      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat C_H'\gets H$
      \If{$C_H' = \top$}
        \State \Return $\Store[m]$
      \EndIf
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H', m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}

  \begin{algorithmic}[1]
    \Function{\Store}{$m$}
      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
      \If{$m = \bot$}
        \State \Return $\bot$
      \EndIf
      \State Store $m$ to disk.
      \State \Return $\top$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
  \caption{\label{SPORFwd}%
    The \(\Fwd\) algorithm forwards \(m\) down the route \(H\), obtained 
    by decrypting \(C_H\) with the node's associated private key.
    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
    is intended for the local node and \(c_m\) is instead sent to disk using 
    \(\Store\).% (\cref{SPORRecv}).%
  }
\end{figure}
